%!TEX program = xelatex
\documentclass[table, aspectratio=169]{beamer}

\usetheme{Template}

\title{Search for New Heavy Gauge Bosons with ATLAS}
%\subtitle{Using all 2016 DS1 data from the 10/06 GRL}
\author{\underline{Ellis Kay}}
\institute{HEP Christmas Meeting 18/12/17}

\addtobeamertemplate{title page}{}{\color{TemplateGrey} \vspace{220pt}\begin{center}Supervisors: Uta Klein \& Carl Gwilliam\end{center}}

\date{ellis.kay@cern.ch}

\setcounter{showSlideNumbers}{1}

\begin{document}
	\setcounter{showProgressBar}{0}
	\setcounter{showSlideNumbers}{0}

	\frame{\titlepage}
	

	\setcounter{framenumber}{0}
	\setcounter{showProgressBar}{1}
	\setcounter{showSlideNumbers}{1}
	
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%  SLIDES  %%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\input{Slides/Introduction}
	
	\input{Slides/AnalysisStrategy2}

	\input{Slides/TheoreticalUncertainties}
	
	\input{Slides/PublishedLimits}
	
	\input{Slides/HeavyVectorTriplet}
	
	\input{Slides/CombinationMotivation}
	
	\input{Slides/StatTools}
	
	\input{Slides/HVTLimits}
	
	\input{Slides/Conclusion}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%  BACKUP  %%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\beginbackup
	\setcounter{showSlideTotal}{0}
	\section{Backup}
	\input{Slides/Selections}
	\input{Slides/MCSamples}
	\input{Slides/SignalReweighting}
	\input{Slides/RealsFakes}
	\input{Slides/Extrapolation}
	\input{Slides/Yields}
	\input{Slides/Systematics}
	\input{Slides/MyResults}
	\input{Slides/MC}
	\input{Slides/Hessian}
	\input{Slides/HERA}
	\input{Slides/ATLASep}
	\input{Slides/PDFChoice}
	\input{Slides/EVs}
	
	\input{Slides/HVT}
	\input{Slides/ResonanceMassDependence}
	\input{Slides/TemplateTruncation}
	\input{Slides/SignalOverlaps}
	%\input{Slides/PlannedTemplates}
	%\input{Slides/DileptonVHVV}
	\input{Slides/MuCalc}
	\input{Slides/RooStatsCheck}
	\input{Slides/Correlations}
	\input{Slides/QCDkFactors}
	\input{Slides/LEPLimits}	
	
	\begin{frame}
		\frametitle{What about the Higgs?}
		
		\li{We are not completely insensitive to $g_{H}$.}
		\lii{In our approximations for $ll$ and $l\nu$ final states (which ignore VBF), $g_{H}$ only enters in xsecs through the width of the \zprime\, and \wprime.}
		\lii{We are insensitive to this because there are many more fermionic degrees of freedom ($N_{F}$) than there are bosonic ones ($N_{B}$) into which the \zprime\, and \wprime\, can decay. The width goes roughly $N_{F}^{2}g_{F}^{2}+N_{B}^{2}g_{H}^{2}$. Since the first term is almost always much larger, the second has a small effect. the exception would be $g_{q}, g_{l} << g_{H}$, but in that case our xsec would be too small.}

	\li{The \wprime\, and \zprime\, have large masses $M_{0}$, which are not related to the Higgs mechanism EWSB, but there is also a small contribution to the masses proportional to $g_{H}^{2}$. The decay into dibosons and thus the (mild) dependence on $g_{H}$ is completely correlated with this.}
	\lii{This is not relevant for us, but in Higgsless models there is another form of the Higgs mechanism and EWSB. The formulation is different, but there are similar egfects including decay into the SM gauge bosons. Basically the physics in that case is the same as if we had a very heavy Higgs boson.}
	
	\end{frame}
	%%%%%%%%%%%%%%%%%%%%%%%
	\backupend
	%%%%%%%%%%%%%%%%%%%%%%%
	
\end{document}






		

		